Corotating Clumps Around Adolescent Low-Mass Stars: Four Years of Complex Quasiperiodic Variables from TESS

### 2023-08-11 paper/ms.tex
update ms

For the SED fitting, we used \texttt{astroARIADNE}
\citep{2022MNRAS.513.2719V}.  We adopted the BT-Settl stellar
atmosphere models \citep{Allard2012} assuming the
\citet{2009ARA&A..47..481A} solar abundances, and the
\citet{2006MNRAS.368.1087B} water line lists.  The broadband
magnitudes we considered included $GG_{\rm BP}G_{\rm RP}$ from Gaia
DR2, $Vgri$ from APASS, $JHK_{\rm S}$ from 2MASS, SDSS $riz$, and the
WISE 1-2 passbands.  We specifically omitted UV flux measurements from
our SED fit to avoid any possible bias induced by chromospheric UV
excess; we similarly omitted WISE 3-4, but due to reliability
concerns.
\texttt{astroARIADNE} compares the measured broadband flux
measurements against pre-computed model grids, and by default fits for
six parameters: $\{ T_{\rm eff}, R_\star, A_{\rm V}, \log g, [{\rm
Fe/H}], d \}$.  The distance  prior is drawn from
\citet{2021AJ....161..147B}.  The surface gravity and metallicity are
generally unconstrained.  And finally, given our particular use-case,
we assumed the following priors for the temperature, stellar size, and
extinction:
\begin{align}
  T_{\rm eff} / {\rm K}    &\sim \mathcal{N}(3000, 1000), \\
  R_\star / R_\odot  &\sim \mathcal{T}_{\rm N}(0.5, 0.3, 0.1, 1.5), \\
  A_{\rm V} / {\rm mag}    &\sim \mathcal{U}(0, 0.2),
\end{align}
for $\mathcal{N}$ the Gaussian and $\mathcal{U}$ the uniform
distributions, and $\mathcal{T}(\mu, \sigma, a, b)$ a truncated normal
distribution with mean $\mu$, standard deviation $\sigma$, and lower
and upper bounds $a$ and $b$.  Using \texttt{Dynesty}
\citep{2020MNRAS.493.3132S}, we statically sampled the posterior
probability assuming the default Gaussian likelihood, and set a
stopping threshold of ${\rm d}\log \mathcal{Z} < 0.01$, where
$\mathcal{Z}$ denotes the evidence.

>>>>

For the SED fitting, we used \texttt{astroARIADNE}
\citep{2022MNRAS.513.2719V}.  We adopted the BT-Settl stellar
atmosphere models \citep{Allard2012} assuming the
\citet{2009ARA&A..47..481A} solar abundances, and the
\citet{2006MNRAS.368.1087B} water line lists.  The broadband
magnitudes we considered included $GG_{\rm BP}G_{\rm RP}$ from Gaia
DR2, $Vgri$ from APASS, $JHK_{\rm S}$ from 2MASS, SDSS $riz$, and the
WISE 1-2 passbands.  We specifically omitted UV flux measurements from
our SED fit to avoid any possible bias induced by chromospheric UV
excess; we similarly omitted WISE 3-4, but due to reliability
concerns.
\texttt{astroARIADNE} compares the measured broadband flux
measurements against pre-computed model grids, and by default fits for
six parameters: $\{ T_{\rm eff}, R_\star, A_{\rm V}, \log g, [{\rm
Fe/H}], d \}$.  The distance  prior is drawn from
\citet{2021AJ....161..147B}.  The surface gravity and metallicity are
generally unconstrained.  And finally, given our particular use-case,
we assumed the following priors for the temperature, stellar size, and
extinction:
\begin{align}
  T_{\rm eff} / {\rm K}    &\sim \mathcal{N}(3000, 1000), \\
  R_\star / R_\odot  &\sim \mathcal{T}_{\rm N}(0.5, 0.3, 0.1, 1.5), \\
  A_{\rm V} / {\rm mag}    &\sim \mathcal{U}(0, 0.2),
\end{align}
for $\mathcal{N}$ the Gaussian and $\mathcal{U}$ the uniform
distributions, and $\mathcal{T}(\mu, \sigma, a, b)$ a truncated normal
distribution with mean $\mu$, standard deviation $\sigma$, and lower
and upper bounds $a$ and $b$.  We validated our chosen upper bound on
$A_{\rm V}$ using a 2MASS color-color diagram.  Finally, using
\texttt{Dynesty} \citep{2020MNRAS.493.3132S}, we statically sampled
the posterior probability assuming the default Gaussian likelihood,
and set a stopping threshold of ${\rm d}\log \mathcal{Z} < 0.01$,
where $\mathcal{Z}$ denotes the evidence.
